\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
glitches + fixups

Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
  function.
The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
\begin{eqnarray}
  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: X \mapsto 2^X, \hspace{.5em} x \mapsto \{h\in X |
f(z)  \ge f(x) + \langle h, z - x\rangle \forall z \in X\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. Given $\tau > 0$, the function
\begin{eqnarray}
  \prox_{\tau f}: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
  \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + \tau f(z),
\end{eqnarray}

@@

\subsection{Our contribution}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
  \epsilon$)-equilibria (in a sense to be made clear later) for
  sequential two-person zero-sum games with imcomplete information and
  perfect recall.

@@

\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients. The idea
is to replace the usual optimality characterization ``$x$ optimal iff
$0 \in \partial f(x)$'' with ``$x$ approx optimal iff $0 \in
\partial_\epsilon f(x)$''. In fact, letting $\epsilon \rightarrow 0^+$,
$\partial f(x) = \partial_{0^+}f(x)$ will coincide with
subgradient of $f$ at $x$.

\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ the set-valued function
\begin{eqnarray}
\partial_\epsilon f: X \mapsto 2^X, \hspace{.5em} x \mapsto \{h\in X |
f(z) + \epsilon \ge f(x) + \langle h, z - x\rangle \forall z \in X\}.
\end{eqnarray}
\end{definition}

@@

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium is a pair $(x^*, y^*)$ of realization
plans such that there exists dual vectors $p^*$ and $q^*$ and a
pertubation vector $v^*$ for which
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
\end{eqnarray}
\end{definition}

>>>>

Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
  function.
The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
\begin{eqnarray}
  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{h\in \mathbb{R}^n | f(z)  \ge f(x) + \langle h, z - x\rangle \forall
z \in X\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. Given $\tau > 0$, the function
\begin{eqnarray}
  \prox_{\tau f}: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
  \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + \tau f(z),
\end{eqnarray}

@@

\subsection{Our contribution}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
  \epsilon$)-equilibria (in a sense to be made clear later in
  Definition \ref{thm:cool_notion}) for
  sequential two-person zero-sum games with imcomplete information and
  perfect recall.

@@

\subsection{Relaxing the conditions for equilibrium}
Let us first introduce the notion of $\epsilon$-subgradients.

\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ the set-valued function
\begin{eqnarray}
\partial_\epsilon f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x
\mapsto \{h \in \mathbb{R}^n | f(z) + \epsilon \ge f(x) + \langle h, z
- x\rangle \forall z \in X\}.
\end{eqnarray}
\end{definition}

The idea is to replace the usual necessary condition ``$0 \in \partial
f(x)$'' for the optimality of $x$ with ``$v \in \partial_\epsilon
f(x)$, for some small perturbation vector $v$''. In fact, it is easy
to see that, for each $x \in X$, $(\partial_\epsilon f(x))_{\epsilon >
  0}$ is a decreasing sequence of sets which converges to $\partial
f(x)$.

Henceforth, the notion of approximate Nash equilibria will be
understood in the following sense.

@@

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium is a pair $(x^*, y^*)$ of realization
plans such that there exists dual vectors $p^*$ and $q^*$ and a
pertubation vector $v^*$ for which
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
\end{eqnarray}
\label{thm:cool_notion}
\end{definition}
